Finite-state morphological transducers for three Kipchak languages

### 2013-10-10 kipchak-lrec-2013/kipchak-paper.tex
more
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@47969 72bbbca6-d526-0410-a7d9-f06f51895060
futwork
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@47974 72bbbca6-d526-0410-a7d9-f06f51895060
some aper update
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@47980 72bbbca6-d526-0410-a7d9-f06f51895060

\usepackage{fontspec}
\usepackage{xunicode}
\usepackage{xltxtra}
\usepackage{natbib}

@@

@@

@@

@@

\bibliographystyle{lrec2012}
\bibliography{paper}

>>>>

\usepackage{fontspec}
\usepackage{xunicode}
\usepackage{xltxtra}
\usepackage{natbib}
\usepackage{multirow}

@@

\cite{bammatov1960}

@@

\begin{table}
\begin{center}
\begin{tabular}{lrrr}
		\hline
\multirow{2}{*}{\textbf{Part of speech}} & \multicolumn{3}{|c|}{\textbf{Number of stems}} \\
                        & Kazakh & Tatar & Kumyk \\
		\hline
		Noun & - & - & - \\
		Verb & - & - & - \\
		Adjective & - & - & - \\
		Proper noun & - & - & - \\
		Adverb & - & - & - \\
		Numeral & - & - & - \\
		Conjunction & - & - & - \\
		Postposition & - & - & - \\
		Pronoun & - & - & - \\
		Determiner & - & - & - \\
		\hline
		Total: & - & - & - \\
		\hline
\end{tabular}
\end{center}

\end{table}

\begin{table}
\begin{center}
\begin{tabular}{lr}
\textbf{Language} & - \\
\hline
Kazakh & - \\
Tatar & - \\
Kumyk & - \\
\hline
\end{tabular}
 \caption{Naïve coverage}
 \label{table:coverage}
\end{center}
\end{table}

\begin{table}
\begin{center}
\begin{tabular}{lrr}
\textbf{Language} & \textbf{Precision} & \textbf{Recall} \\
\hline
Kazakh & - &  - \\
Tatar & - & - \\
Kumyk & - & - \\
\hline
\end{tabular}
 \caption{Precision and recall}
 \label{table:coverage}
\end{center}
\end{table}

@@

%Code switching
%More languages

@@

\bibliographystyle{apalike}

\bibliography{kipchak-paper}
